General constraints on magic state protocols from the statistical mechanics of \\Wigner negativity

### 2021-06-09 magic_paper.tex
minor canges

\input{preamble}

\begin{document}
% Labels and Refs (consistency, cref vs ref, thm vs lem vs prop, ??)
% Figs check(fig.0, move to app, consistency, cbars, iffalse, axes)

% Notation consistency (noise vs error, \ln{} -> \ln, \ln vs \log vs \log_2, italics & \emph, Aberg -> {\AA}berg, quasi-dist vs quasi-prob dist)
% UK vs US english
% Spacing (figs, sections, paragraphs, eq. numbering, \noindent, QEDs)

@@

This figure includes numerical estimates of the optimal majorization bounds $R_{\rm{num}}$ obtained by considering the full Lorenz curve, which show that the first elbow constraint can be further improved.
\begin{figure}[t]
    \centering
    \includegraphics[scale=0.35]{figs/distill_bounds.pdf}
    \caption{\textbf{Distillation bounds in the unital fragment.} Distillation bounds obtained by the first elbow majorisation constraint $R$, mana $\M$ and max--thauma $\theta_{\rm{max}}$ are plotted for $\epsilon' = 0$, up to error $\epsilon = 3/7$.
    Majorisation provides stricter rates than the global mana and max--thauma bounds.
    Numerical bounds $R_{\rm{num}}$ obtained by full Lorenz curve comparison for some Strange state purification processes with even number of copies $m,n \leq 30$ highlight that the first elbow constraint can be improved.
    }
    \label{fig:distill_bounds}
\end{figure}

@@

	We have the following family of upper bounds on the magic distillation rate $R := m/n$,
	\begin{equation}
		R \leq \frac{F_\alpha(W_\rho) - F_\alpha(W_\tau)}{F_\alpha(W_{\rho'}) - F_\alpha(W_{\tau'})},
	\end{equation}
	where $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$ and $\beta F_\alpha(W_\rho) := D_\alpha (W_\rho || W_\tau) - \log \Z$ is the $\alpha$--free energy of the Wigner distribution. 
\end{theorem}
For magic protocols that generate unital maps the above bound reduces to the simpler form
\begin{equation}
	R \leq \frac{2\log d - H_{\alpha}(W_\rho)}{2\log d - H_{\alpha}(W_{\rho'})}.
\end{equation}
In particular for the case of noisy Strange states on qutrits and $\epsilon'=0$, this bound becomes
\begin{equation}
	R \leq \frac{2(1-\alpha)\log 3 - \log \left [8(\frac{1}{6} - \frac{\epsilon}{18})^\alpha + (-\frac{1}{3} + \frac{4\epsilon}{9})^\alpha\right ] }{2(1-\alpha)\log 3 + \alpha \log 6 - \log (8 + 2^\alpha )}.
\end{equation}
For any $\epsilon$ the upper bound can be numerically minimized over $\alpha$.
\begin{figure}[t!]
    \centering
    \subfigure[][]{%
    \label{fig:Ra}%
    \includegraphics[scale=0.4]{figs/Ra_vs_a_eps.pdf}}\\
    \subfigure[][]{%
    \label{fig:RaDiff}%
    \includegraphics[scale=0.4]{figs/RaDiff_vs_a_eps.pdf}}
    \caption{$R_\alpha$ and $R_\alpha - R_{\infty}$ for the Strange state distillation in the unital fragment
    \nick{Can compare thauma and mana for other magic states now more easily}}
    \label{fig:rate_a_contour}
\end{figure}

>>>>

\input{preamble}
% Labels and Refs (consistency, cref vs ref, thm vs lem vs prop, ??)
% Figs check(consistency, cbars, captions, axes, iffalse)
% Notation consistency (noise vs error, \ln{} -> \ln, \ln vs \log vs \log_2, italics & \emph, Aberg -> {\AA}berg, quasi-dist vs quasi-prob dist, def elbows)
% UK vs US english
% Spacing (figs, sections, paragraphs, eq. numbering, \noindent, QEDs)

\begin{document}

@@

This figure includes numerical estimates of the optimal majorization bounds $R_{\rm{num}}$ obtained by considering the full Lorenz curve, which show that the first elbow constraint can be further improved.
\begin{figure}[t]
    \centering
    \includegraphics[scale=0.35]{figs/distill_bounds.pdf}
    \caption{\textbf{Distillation bounds in the unital fragment.} Distillation bounds obtained by the first elbow majorisation constraint $R_{\infty}$, the 10-Renyi bound $R_{10}$,o mana $\M$ and max--thauma $\theta_{\rm{max}}$ are plotted for $\epsilon' = 0$, up to error $\epsilon = 3/7$.
    Majorisation provides stricter rates than the global mana and max--thauma bounds.
    Numerical bounds $R_{\rm{num}}$ obtained by full Lorenz curve comparison for some Strange state purification processes with even number of copies $m,n \leq 30$ highlight that the first elbow constraint can be improved.
    }
    \label{fig:distill_bounds}
\end{figure}

@@

	We have the following family of upper bounds on the magic distillation rate $R := m/n$,
	\begin{equation}
		R \leq \frac{F_\alpha(W_\rho) - F_\alpha(W_\tau)}{F_\alpha(W_{\rho'}) - F_\alpha(W_{\tau'})},
	\end{equation}
	where $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$ and $\beta F_\alpha(W_\rho) := D_\alpha (W_\rho || W_\tau) - \log \Z$ is the $\alpha$--free energy of the Wigner distribution. 
\end{theorem}
For magic protocols that preserve unital maps, the above bound reduces to the simpler form
\begin{equation}
	R \leq \frac{2\log d - H_{\alpha}(W_\rho)}{2\log d - H_{\alpha}(W_{\rho'})}.
\end{equation}
In particular for the case of noisy Strange states on qutrits and $\epsilon'=0$, this bound becomes
\begin{equation}
	R \leq \frac{2(1-\alpha)\log 3 - \log \left [8(\frac{1}{6} - \frac{\epsilon}{18})^\alpha + (-\frac{1}{3} + \frac{4\epsilon}{9})^\alpha\right ] }{2(1-\alpha)\log 3 + \alpha \log 6 - \log (8 + 2^\alpha )}.
\end{equation}
The upper bound can be numerically minimized over $\alpha$, for any $\epsilon$.
\begin{figure}[t!]
    \centering
    \subfigure[][]{%
    \label{fig:Ra}%
    \includegraphics[scale=0.4]{figs/Ra_vs_a_eps.pdf}}\\
    \subfigure[][]{%
    \label{fig:RaDiff}%
    \includegraphics[scale=0.4]{figs/RaDiff_vs_a_eps.pdf}}
    \caption{$R_\alpha$ and $R_\alpha - R_{\infty}$ for the Strange state distillation in the unital fragment
    \nick{Can compare thauma and mana for other magic states now more easily}}
    \label{fig:rate_a_contour}
\end{figure}
